Representation Learning for Generalized Planning - SAT Encodings

### 2020-08-26 doc/encodings/paper.tex
Implement an adaptive value for the upper bound on V(s)

Encoding is parametrized by
\begin{itemize}
 \item Pool $F$ of description logic features $f$, each with given feature complexity $\mathcal{K}(f)$.
 \item Training set consisting of a sample of transitions from a number of instances of the same domain.
       At the moment we're assuming the sample is complete, and we have full information on whether each state
       in the sample is a goal state, an unsolvable state, or otherwise (see below for definitions). We also have access
       to the minimum distance to a goal $V^*(s)$ for each state $s$.
 \item $D$: maximum allowed value for $V(s)$ for any $s$ in the training set.\footnote{This is to be improved based on $V^*(s)$.}
\end{itemize}

@@

 \item $V(s) \leq d$ for $s$ alive, and $d \in [0, D]$.
 Note that for states $s$ that are a goal, we know $V(s)=0$, hence $V(s) \leq d$ for all $d$,
 and for states $s$ that are unsolvable, we know that $V(s) \not\leq d$ for all $d$.
 Thus, we can restrict SAT variables $V(s) \leq d$ to those states $s$ that are alive.

@@

>>>>

Encoding is parametrized by
\begin{itemize}
 \item Pool $F$ of description logic features $f$, each with given feature complexity $\mathcal{K}(f)$.
 \item Training set consisting of a sample of transitions from a number of instances of the same domain.
       At the moment we're assuming the sample is complete, and we have full information on whether each state
       in the sample is a goal state, an unsolvable state, or otherwise (see below for definitions). We also have access
       to the minimum distance to a goal $V^*(s)$ for each state $s$.
 \item A parameter $\delta$ which is a ``slack'' value to determine the maximum deviation from the optimal $V^*(s)$
 what we will allow in our policy. This will be made clearer in the encoding below.
\end{itemize}

@@

 \item $V(s) \leq d$ for $s$ alive, and $d \in [0, D]$, where $D = \max_{s} \delta \cdot V^*(s)$.
 Note that for states $s$ that are a goal, we know $V(s)=0$, hence $V(s) \leq d$ for all $d$,
 and for states $s$ that are unsolvable, we know that $V(s) \not\leq d$ for all $d$.
 Thus, we can restrict SAT variables $V(s) \leq d$ to those states $s$ that are alive.

@@

\smallpar{C10}
$V(s)$ cannot be much larger than $V^+(s)$:
\begin{align}
 V(s) \leq \delta \cdot V^*(s),&\;\; \text{for $s$ alive.}
\end{align}
